Meta-analysis

### 2019-10-22 05_MetaAnalysis.Rmd
Investigations for what contributes to yield volatility

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
source("R/import_data.R")
```

@@

Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
```{r}
source("R/yield_volatility.r") #function to investigate the volatility in yields

@@

```{r}
experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)

@@

rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
   experiment_sites[experiment_sites$location == "NGA - Premer",c("lat","lon")]

@@

@@

@@

>>>>

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
library(bomrang)
source("R/import_data.R")
```

@@

Host genotype seems to contribute to the variation in yield. Berken shows higher yields compared to crystal and jade.
```{r yield_vol}
source("R/yield_volatility.r") #function to investigate the volatility in yields

@@

```{r yield_from_rain}
experiment_sites <- read.csv("data/Mungbean_experiment_sites.csv", stringsAsFactors = FALSE)

@@

# sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lon")]
# closest weather to Premer does not have rain, recoding so it takes the next closest station
rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")] <- 
   sweep_for_stations(latlon = unlist(c(rain_dat_sum[rain_dat_sum$location == "Premer", c("lat","lon")])))[2,c("lat","lon")]

@@

rain_dat_sum[rain_dat_sum$location == "Dalby", c("lat","lon")] <- c(-27.168426, 151.264421)

rain_dat_sum$rainfall_sum <- NA

@@

# loop to download and save all the rainfall sum data

for(j in -10:20){
   if(j == -10){lm_data <- data.frame()}

   for(i in seq_along(rain_dat_sum$trial_ref)){

      #ERROR HANDLING
     # possibleError <- tryCatch(
         rain_dat_sum$rainfall_sum[i] <- 
            AUS_rainfall(StartDate = as.Date(rain_dat_sum$planting_date)[i] + 10,
                         EndDate = as.Date(rain_dat_sum$planting_date)[i] + 90,
                         lat = rain_dat_sum$lat[i],
                         long = rain_dat_sum$lon[i])
         #error=function(e) e
         #)

      #if(inherits(possibleError, "error")) {print(possibleError)
      #   next
      }
   }

   lmod1 <- summary(lm(rainfall_sum ~ grain_yield, 
                       data = rain_dat_sum[rain_dat_sum$location != "Hermitage",])) # remove hermitage which is irrigated

   lm_data <- rbind(lm_data,
                    data.frame(days_from_plant = 10,
                               estimate = coef(lmod1)[2,1],
                               P_value = coef(lmod1)[2,4],
                               r_squared = lmod1$r.squared,
                               adj_r_squared = lmod1$adj.r.squared,
                               stringsAsFactors = FALSE)
                    )

write.csv(lm_data, "data/rainfall_x_Gyield_lmod.csv")
<- read.csv("data/rainfall_x_Gyield_lmod.csv", stringsAsFactors = FALSE)
rain_dat_sum[rain_dat_sum$location != "Hermitage",] %>%
   ggplot(aes(x = rainfall_sum, y = grain_yield )) + 
   geom_point(aes(colour = location)) +
   geom_smooth(method = "lm")

@@

is.vector(unlist(c(rain_dat_sum[1,5],rain_dat_sum[1,6])))

plot(P_value ~ days_from_plant, data = lm_data)
plot(r_squared ~ days_from_plant, data = lm_data)
plot(estimate ~ days_from_plant, data = lm_data)

tmp1 <- read.csv("C:/Users/U8011054/AppData/Local/Temp/RtmpkbEvfL/IDCJAC0009_041359_1800_Data.csv", stringsAsFactors = FALSE)

nchar(tmp1$Bureau.of.Meteorology.station.number[1])
strsp

head(tmp1)
message()
